Verifying Demonstrations

### 2018-02-27 paper/protocol.tex
Changes to \S?PK optional notation

\section{PRIVO: A protocol for protest outcome verification}

@@

\begin{figure*}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets \PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon &
        \DBPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}} \\
      W\colon & wid\gets \PRF_{k_W}(pid), \\
        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
        & \pi_W = \SPK{k_W, \sigma_W}
          {wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
            \Sign[k]{k_W}}{pid, wid, t_s, l, wsig} \\
      P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
        & \pi_P = \SPK{k_P, \sigma_P}{pid = \PRF_{k_P}(cid), \sigma_P = 
          \Sign[k]{k_P}}{pid, wid, t_s, l, wsig}
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure*}

@@

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \enquote{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest (cause).
(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)

>>>>

\section{PRIVO: A protocol for protest outcome verification}
\label{protocol}

@@

\begin{figure*}
  \centering
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & cid\gets H(\text{manifesto}), \\
        & pid\gets \PRF_{k_P}(cid) \\
      P\to W\colon & pid \\
      W\leftrightarrow P\colon &
        \DBPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = \Sign[k]{k_P}] \\
      W\colon & wid\gets \PRF_{k_W}(pid), \\
        & wsig\gets \PRF_{k_W}(wid, t_s, l) \\
      W\to P\colon & (wid, t_s, l, wsig) \\
      W\to S\colon & H(pid, wid, t_s, l, wsig) \\
      P\to S\colon & H(pid, wid, t_s, l, wsig) \\
      W\to S\colon & (pid, wid, t_s, l, wsig, \pi_W),\quad \text{where}\\
        & \pi_W = \SPK[k_W, \sigma_W]%
          [wid = \PRF_{k_W}(pid), wsig = \PRF_{k_W}(wid, t_s, l), \sigma_W = 
            \Sign[k]{k_W}][pid, wid, t_s, l, wsig] \\
      P\to S\colon & (pid, wid, t_s, l, wsig, \pi_P),\quad \text{where}\\
        & \pi_P = \SPK[k_P, \sigma_P][pid = \PRF_{k_P}(cid), \sigma_P = 
          \Sign[k]{k_P}][pid, wid, t_s, l, wsig]
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of message exchanges.
    The organizer \(O\) broadcasts the manifesto.
    \(P\), \(W\) and their computations are as in \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to the storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure*}

@@

We will start with the latter.
The identifier of the protest must be regulated, for the same reasons as for the 
user identifiers --- otherwise a counter-protest can simply choose the same 
protest identifier.
As was pointed out in \cref{CauseIsTheCommonDenominator}, the cause is at the 
root of what defines a protest.
The cause can be captured in some sort of \emph{manifesto}, thus, we will use 
the hash value of the manifesto as identifier of the protest (cause).
(As shown as manifesto and cause identifier \(cid\) in \cref{fig:ProofFig}.)
